---
title: "Daily Average Temperature"
author: "Andrés Bishop"
date: "2018"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Overview

"Daily Average Temperature" is my very first simple shiny app that shows average daily temperature from three cities in Catalonia in a time span of 1 to 60 days. The user can choose the beginning day, the numbert of days to display and the city from which data comes from. The data is showed in a line graphic, using the plotly library.

## Data Acquisition

Data is acquired from the DAILY GLOBAL HISTORICAL CLIMATOLOGY NETWORK (GHCN-DAILY) Version 3.22 of the NOAA National Climatic Data Center (http://doi.org/10.7289/V5D21VHZ) using the rnoaa library and filtered to obtain data frames with the following data:
  
  ```{r, echo=FALSE, warning=FALSE, message=FALSE, cache=FALSE, results=TRUE, prompt=FALSE, source=TRUE, include=TRUE}
library(plotly)
library("rnoaa")
knitr::opts_knit$set(progress = FALSE, verbose = FALSE)
Reus<-ghcnd(stationid = "SPE00120530")
monitorsReus <- Reus$id
all_monitors_clean <- meteo_pull_monitors(monitorsReus,
                                          date_min = "2016-03-01",
                                          date_max = "2016-03-31") %>%
  rename(day = date,
         location = id)
plotReus<-all_monitors_clean[,c(2:6)]
plotReus["Station"]<-"Reus"
plotReus$tmax <- plotReus$tmax/10
plotReus$tmin <- plotReus$tmin/10
plotReus$tavg <- plotReus$tavg/10
plotReus %>% head() %>% knitr::kable()
```

## Plotting the data

```{r, echo=FALSE, warning=FALSE, message=FALSE, cache=FALSE, results=TRUE, prompt=FALSE, source=FALSE, include=TRUE}

library("plotly")
library("rnoaa")
library("webshot")
 p <- plot_ly(plotReus, x = ~day, y = ~tavg, color = ~Station, type = 'scatter', mode = 'lines', 
               showlegend = TRUE )%>%
  layout(title = "Average Temperatures in Reus (Spain)",
         paper_bgcolor='rgb(255,255,255)', plot_bgcolor='rgb(229,229,229)',
         xaxis = list(title = "Days",
                      gridcolor = 'rgb(255,255,255)',
                      showgrid = TRUE,
                      showline = FALSE,
                      tickcolor = 'rgb(127,127,127)',
                      ticks = 'outside',
                      zeroline = FALSE),
         yaxis = list(title = "Temperature (degrees C)",
                      gridcolor = 'rgb(255,255,255)',
                      showgrid = TRUE,
                      showline = FALSE,
                      tickcolor = 'rgb(127,127,127)',
                      ticks = 'outside',
                      zeroline = FALSE))
```
```{r, echo=FALSE, warning=FALSE, message=FALSE, cache=FALSE, results=TRUE, prompt=FALSE, source=TRUE, include=TRUE}
p
```

## Fin

Thank you!
